### 2019-02-14 2-Chapters/3-Chapter/SMPyBandits_paper.git/paper.tex
Clean up doubles in the huge BibTeX file.

Multi-Armed Bandit (MAB) problems are well-studied sequential decision
making problems in which an agent repeatedly chooses an action (the
``\emph{arm}'' of a one-armed bandit) in order to maximize some total
reward \citep{Robbins52}, \citep{LaiRobbins85}. Initial motivation for
their study came from the modeling of clinical trials, as early as 1933
with the seminal work of Thompson \citep{Thompson33}, where arms
correspond to different treatments with unknown, random effect. Since
then, MAB models have been proved useful for many more applications,
that range from cognitive radio \citep{Jouini09} to online content
optimization like news article recommendation \citep{Li10}, online
advertising \citep{LiChapelle11}, A/B Testing \citep{Kaufmann14,Jamieson17}, or portfolio optimization \citep{Sani12}.

>>>>

Multi-Armed Bandit (MAB) problems are well-studied sequential decision
making problems in which an agent repeatedly chooses an action (the
``\emph{arm}'' of a one-armed bandit) in order to maximize some total
reward \citep{Robbins52}, \citep{LaiRobbins85}. Initial motivation for
their study came from the modeling of clinical trials, as early as 1933
with the seminal work of Thompson \citep{Thompson33}, where arms
correspond to different treatments with unknown, random effect. Since
then, MAB models have been proved useful for many more applications,
that range from cognitive radio \citep{Jouini09} to online content
optimization like news article recommendation \citep{Li10}, online
advertising \citep{LiChapelle11}, A/B Testing \citep{Kaufmann14,Jamieson17ABTest}, or portfolio optimization \citep{Sani12}.

### 2019-02-14 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Clean up doubles in the huge BibTeX file.

Efficient Medium Access (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this Section, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, used in combination with a time-frequency slotted ALOHA-based protocol.
We consider the Upper-Confidence Bound (\UCB) \cite{Auer02}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12}.
% Both algorithms have already been applied with success, for Opportunistic Spectrum Access \cite{Jouini10} and recently for multi-users Cognitive Radio problems \cite{Toldov16}.

@@

%This section presents the formalism of the Multi-Armed Bandit (MAB) problem, as introduced by \cite{LaiRobbins85}, and two classical algorithms designed to tackle its simplest version (stochastic MAB), \UCB{} from \cite{Auer02} and Thompson Sampling from \cite{Thompson33,Kaufmann12}.
%For more details, \cite{Bubeck12} is an excellent review.

>>>>

Efficient Medium Access (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this Section, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, used in combination with a time-frequency slotted ALOHA-based protocol.
We consider the Upper-Confidence Bound (\UCB) \cite{Auer02}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12Thompson}.
% Both algorithms have already been applied with success, for Opportunistic Spectrum Access \cite{Jouini10} and recently for multi-users Cognitive Radio problems \cite{Toldov16}.

@@

%This section presents the formalism of the Multi-Armed Bandit (MAB) problem, as introduced by \cite{LaiRobbins85}, and two classical algorithms designed to tackle its simplest version (stochastic MAB), \UCB{} from \cite{Auer02} and Thompson Sampling from \cite{Thompson33,Kaufmann12Thompson}.
%For more details, \cite{Bubeck12} is an excellent review.

### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Clean up doubles in the huge BibTeX file.

The TS algorithm, although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12}.
It is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including on problems from Cognitive Radio \cite{Toldov16,Mitton16}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.

>>>>

The TS algorithm, although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12Thompson}.
It is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including on problems from Cognitive Radio \cite{Toldov16,Mitton16}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.
